--- 
title: "WUP_08"
author: "Giovanni Asencio"
output: html_document
---

# Introduction

This project compares two regression models for predicting a bear's age.

# Load Data

```{r}
bears <- read.csv("BEARS.csv", header=TRUE)
```

# Model 1: AGE ~ LENGTH

```{r}
M1 <- lm(AGE ~ LENGTH, data=bears)

plot(AGE ~ LENGTH, data=bears)

abline(M1)

summary(M1)
```

The graph above shows the relationship between AGE and LENGTH. The adjusted R-squared value is 0.5073, meaning that about 50.73% of the variation in AGE is explained by LENGTH.

# Model 2: AGE ~ NECK

```{r}
M2 <- lm(AGE ~ NECK, data=bears)

plot(AGE ~ NECK, data=bears)

abline(M2)

summary(M2)
```

The graph above shows the relationship between AGE and NECK. The adjusted R-squared value is 0.5041, meaning that about 50.41% of the variation in AGE is explained by NECK.

# Comparison

The AGE ~ LENGTH model has an adjusted R-squared of 0.5073, while the AGE ~ NECK model has an adjusted R-squared of 0.5041. Since 0.5073 is slightly larger than 0.5041, the AGE ~ LENGTH model is the better predictor of AGE.

# Conclusion

Both LENGTH and NECK are useful predictors of AGE. However, the AGE ~ LENGTH model performs slightly better because it has the larger adjusted R-squared value. Therefore, AGE ~ LENGTH is the preferred model for predicting a bear's age.
